# Method

This section describes the zoning standard and the analysis method. This may
be the bulk of the paper.

## Zoning standard

Describe the zoning standard

### Core constraints

OZFS begins with a set  of core constraints: components that are necessary to 
establish the maximum allowable bulking or building envelope on any lot. Our 
work-in-progress list of these constraints are captured within an Airtable 
titled [OZFS schema](https://airtable.com/invite/l?inviteId=invIE9Rq8BJxoRZe9&inviteToken=c24d20d82c00f933e02ca4d7f9b78088b2eaefcef049f3691df85eb48f858fbc&utm_medium=email&utm_source=product_team&utm_content=transactional-alerts). (NOTE: Do I need to create an account to access this???) 

Each constraint is categorized into a core component of what is known as bulking, which is the process through which structures take their form on a lot within the modern-day zoning concept (the bucket is titled "core bulking component"). OpenZoning considers these components to be the core devices through which modern society has used zoning to conceptualize and abstract the tangible resource of land as discrete containers for bulks, i.e. structures and buildings. These containers are called lots -- discrete areas of land plus the volumes of air above and earth beneath them -- and are the base units of zoning. When applied to the lot, modern society's conceptualization of land is executed through a set of components meant to control the realization of bulks (i.e. bulking) on these lots. They are:

- buildable area limits
- height limits 
- structure envelopes
- number of structures
- types of structures
- relationship between structures
- number of units limits
- types of floor use

This list is a work in progress, and correctly identifying these components is essential to OpenZoning's goal of creating a standard machine-readable format that can accomodate the wide swathe of zoning codes that exist across America, and across the world. 

## Analysis of accessory dwelling unit capacity

Describe both a naive approach that would be the best you can do with other methods
and the approach we could take with this data.

### Naive approach

Best you could do with a spreadsheet

### Proposed approach

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
